\cvsection{Research Experience}
\begin{cventries}
  \cventry
    {Mentor: Prof. Gaurav Pandey, Dept. of EE, IIT Kanpur}
    {Blind Image Quality Assessment}
    {IIT Kanpur}
    {December'16 - January'17}
    {
      \begin{cvitems}
        \item {Objective: To calculate Image Quality score by learning a coupled dictionary}
        \item {\textbf{Unsupervised learning of coupled dictionary} from the set of patches taken from pristine natural images and distorted images (BLUR, JPEG, JP2K, AWGN) (LIVE public-domain database).}
        \item {Using \textbf{regression algorithms} like lasso to optimize the training stage for deriving the dictionary pair, sparse coefficients, and the projection matrices of common feature space.}
        \item {Proposed an algorithm to calculate the \textbf{global quality score} from the energy of the projection matrices of the source domain and target domain sparse coefficients in the common feature space.}
        \item {Applied the coupled dictionary algorithm to synthesize \textbf{super resolution image} from low resolution image }
      \end{cvitems}
    }
  \cventry
    {Mentor: Prof. Tanaya Guha, Dept. of EE, IIT Kanpur}
    {Animated image cloth segmentation}
    {IIT Kanpur}
    {December’15 - October’16}
    {
      \begin{cvitems}
        \item {Objective: To segment the clothes from the animated images and recognise its constituent parts of clothing}
        \item {Used various algorithms for image segmentation like \textbf{edge detection, K-means clustering} and implemented in MATLAB with 60-75\% accuracy at the end of Summer’16.}
        \item {Performed texture based segmentation using multi-channel \textbf{Gabor filters} to remove splitting of same texture region}
        \item {Proposed a novel probabilistic model for parsing animated image using an elegant algorithm, \textbf{Data Driven Markov Chain Monte Carlo (DDMCMC)}, and applying \textbf{split and merge method} to get its optimal solution.}
      \end{cvitems}
    }

\end{cventries}
